The Dynamics of Anthropomorphic Effects in Human-Robot Interaction

### 2014-03-24 paper.tex

A phenomenon that is often studied related to the human-like design of robots is
\textbf{anthropomorphism}. Besides a feeling of affinity, and empathy,
anthropomorphism can be understood as being one of the resulting (and  more or
less desired) effects of the anthropomorphic design of artificial agents (up to
the first positive peak). The essence of anthropomorphism is the human user's
perception of human-likeness in the non-human agent. Logically, anthropomorphism
is said to be enhanced with increased human-like design of the agent. There are
various other reasons and explanations for why people tend to anthropomorphize
non-human agents. In general, as anthropomorphism emerges in a (real or
imagined) interaction \citep{persson_anthropomorphism_2000} between at least two
players (the human who anthropomorphizes and the non-human agent which is
anthropomorphized) there are also two main perspectives on the phenomenon: an
artifact-centered (design) and a human-centered (cognitive, psychological) one.
The Uncanny Valley hypothesis can be categorized as being part of first,
artifact-centered approach, to understand anthropomorphism.

@@

@@

%The gathered data for these aspects include qualitative observations,
%semi-structured interviews, and also quantitative assessments of various
%aspects of human-robot interaction.

@@

%    \begin{tikzpicture}[scale=0.5, y = 2cm]
%    %axis
%    \draw (0,0) -- coordinate (x axis mid) (20,0);
%    \draw (0,0) -- coordinate (y axis mid) (0,7);
%    %ticks
%    \foreach \x in {0,4,...,20}
%        \draw (\x,1pt) -- (\x,-3pt);
%    \foreach \y in {1,...,7} 
%        \draw[black!20] (20,\y) -- (-3pt,\y);
%    \foreach \y in {1,...,7} 
%        \draw (-3pt, \y) node[anchor=east] {\y}; 
%    %labels
%    \node[below=0.8cm] at (x axis mid) {People's perception ($\sigma=15$)};
%    \node at (2, -0.4) {\tiny expectations};
%    \node[align=center] at (6, -0.4) {\tiny after\\ \tiny first usage};
%    \node[align=center] at (10, -0.4) {\tiny after\\ \tiny 2 weeks};
%    \node[align=center] at (14, -0.4) {\tiny after\\ \tiny 2 months};
%    \node[align=center] at (18, -0.4) {\tiny after\\ \tiny 6 months};
%
%    \draw[dashed, black!50] (6,0) -- (6,7) node[sloped, below, pos=0.25] {\tiny novelty effect};
%
%    \draw[ultra thick, red!50] (2,5.6) -- (6,6.1) -- (10,6.3) -- (14,6.3) -- (18,6.1) node at (15,6.5) {\tiny \it ease of use};
%    \draw[ultra thick, purple] (2,4.9) -- (6,5.2) -- (10,5.1) -- (14,4.5) -- (18,4.2) node at (3,4.7) {\tiny \it usefulness};
%    \draw[ultra thick, blue!50] (2,4) -- (6,4.1) -- (10,4.6) -- (14,4.1) -- (18,4.3) node at (16,4) {\tiny \it fun};
%    \draw[ultra thick, green!50] (2,3.9) -- (6,4.1) -- (10,4.2) -- (14,3.8) -- (18,3.3) node at (19,3.5) {\tiny \it intelligence};
%    \draw[ultra thick, orange] (2,3.5) -- (6,4.2) -- (10,4) -- (14,3.2) -- (18,2.8) node at (14,2.7) {\tiny \it impact};
%
%    \draw[ultra thick, dashed] (2,5.2) -- (6,5.2) -- (10,5) -- (14,4.9) -- (18,4.5) node at (14,5.3) {\tiny \it overall};
%
%    \end{tikzpicture}

@@

@@

\begin{enumerate}
    	\item People engage in a more social and human-like way with a robotic pet compared to a functional robot and a tablet computer, therefore there will be a higher amount of anthropomorphic language in the AIBO and Roomba forum, compared to the iPad forum.

@@

\begin{itemize}
    \item \textit{Life-likeness}, such as being alive or having (parts of) a
        body, \eg \textit{``she can be reborn since you copied her memory
        stick''};
    \item \textit{Emotional states, empathy} or the technology having a
        \textit{feeling}, \eg \textit{``oh no, poor AIBO''};
    \item \textit{Gender, personality} or the technology having an
        \textit{intention}, \eg Roomba \textit{``seems to like to hang around
        under the sofa''};
    \item When the author gave the technology a \textit{name}, \eg
        \textit{``whenever I show Java his pink ball''};
    \item Being \textit{socially integrated}, such as being a family member, \eg
        \textit{``I'm considering adding a Roomba to the family''};
    \item \textit{Metaphorical ways}, \eg Roomba \textit{``sings its victory
        song when it finishes and docks''}.
\end{itemize}

@@

@@

In this model, anthropomorphism is quantified by a \emph{normalized level of
anthropomorphic effects}: because anthropomorphic effects are not quantified on
an absolute scale, we present them as a normalized value, that spans from a
minimum (no anthropomorphic effects) to a maximum (corresponding to the novelty
effect peak on Figure~\ref{fig:dynamics}). The actual maximum value of
anthropomorphic effects depends on each unique combination of human, robot and
several other factors we introduce below, and thus varies. The general
\emph{shape} of the model remains however the same and depicts the evolution of
anthropomorphism over time, \ie the general dynamics of anthropomorphism.

@@

%\begin{figure*}[htb]
%\centering
%
%
%\begin{tikzpicture}[scale=1.2]
%
%% background shading
%\path[fill=gray!20] (0,0) rectangle (0.6,5.5);
%\path[fill=gray!50] (0.6,0) rectangle (5.2,5.5);
%\path[fill=gray!20] (5.2,0) rectangle (9.8,5.5);
%\draw(0,5.5) node[anchor=south west] {\scriptsize \sc Initialization};
%\draw(4,5.5) node[anchor=south] {\scriptsize \sc Familiarization};
%\draw(7.5,5.5) node[anchor=south] {\scriptsize \sc Stabilization};
%% horizontal axis
%\draw[->] (0,0) -- (10,0) node[anchor=north] {$t$};
%\draw(5,-0.1) node[anchor=north] {\scriptsize Duration of interaction};
%
%
%% vertical axis
%\draw[->] (0,0) -- (0,6) node[anchor=east] {};
%\draw(-0.8,3) node[rotate=90,anchor=south] {\scriptsize Normalized level of anthropomorphic effects};
%
%\draw (-0.05, 3) -- (0.05, 3) node[anchor=east] {\scriptsize ICA$_{\mathcal B}$};
%\draw (-0.05, 4.1) -- (0.05, 4.1) node[anchor=east] {\scriptsize ICA$_{\mathcal A}$};
%\draw (-0.05, 0.6) -- (0.05, 0.6) node[anchor=east] {\scriptsize ICA$_{\mathcal C}$};
%
%% vertical axis - end
%\draw[->] (9.8,0) -- (9.8,2) node[anchor=east] {};
%\draw (9.8, 0.8) node[anchor=west] {\scriptsize SLA$_\mathcal{E}$};
%\draw (9.8, 1.4) node[anchor=west] {\scriptsize SLA$_\mathcal{D}$};
%\draw (9.8, .2) node[anchor=west] {\scriptsize SLA$_\mathcal{F}$};
%
%
%\draw[<-] (0.65,5) -- (0.8,5.2) node[anchor=east] {};
%\draw (0.9,5.3) node[anchor=west] {\tiny \it novelty effect};
%
%
%\draw[dotted] (0, 5) -- (6.2,5);
%\draw[dotted] (0, 3) -- (6.2,3);
%\draw[<->] (6.1,3) -- (6.1,5) node[anchor=east] {};
%\draw (6.2,4) node[rotate=90, anchor=north] {\tiny Expectation mismatch};
%
%\draw[<-] (1.7,4.4) -- (3.2,4.1) node[anchor=east] {};
%\draw[<-] (2.85,3.3) -- (3.2,4.1) node[anchor=east] {};
%\draw (3.2,4.1) node[anchor=west] {\tiny \it disruptive behaviors};
%%%%%%
%%% CURVES
%%%%%
%\begin{scope}[yscale=-1,shift={(-0.125,-0.4)}]
%
%% output of inkscape2tikz
%\path[draw=black]
%    (0.1250,-2.5620) .. controls (0.1451,-3.7193) and (0.4645,-4.5602) ..
%    (0.7044,-4.5633) .. controls (0.8413,-4.5633) and (0.9599,-4.5104) ..
%    (1.0794,-4.3971) .. controls (1.1989,-4.2841) and (1.3191,-4.1185) ..
%    (1.4588,-3.9181) .. controls (1.5287,-3.8183) and (1.5610,-4.1413) ..
%    (1.6381,-4.1420) .. controls (1.7378,-4.1420) and (1.6515,-3.6434) ..
%    (1.9554,-3.2280) .. controls (2.1466,-2.9667) and (2.3889,-2.7023) ..
%    (2.6819,-2.4292) .. controls (2.7551,-2.3607) and (2.7727,-2.8119) ..
%    (2.8771,-2.8180) .. controls (2.9742,-2.8180) and (2.9594,-2.2108) ..
%    (3.1665,-2.0209) .. controls (3.3340,-1.8673) and (3.5379,-1.7527) ..
%    (3.7508,-1.6236) .. controls (5.8366,-0.4852) and (8.0977,-0.2106) ..
%    (10.1250,-0.1860);
%\path[draw=black, dashed]
%    (0.1250,-3.6924) .. controls (0.1103,-4.0298) and (0.4645,-4.5602) .. 
%    (0.7044,-4.5633)
%    (3.7508,-1.6236) .. controls (4.9579,-0.9555) and (8.1358,-0.8261) .. 
%    (10.1250,-0.7946);
%\path[draw=black,dashed]
%    (0.1250,-0.1953) .. controls (0.1804,-3.3871) and (0.4645,-4.5602) .. 
%    (0.7044,-4.5633) .. controls (0.8413,-4.5633) and (0.9599,-4.5104) .. 
%    (1.0794,-4.3971)
%    (3.7508,-1.6236) .. controls (4.7654,-0.8505) and (6.5955,0.3538) .. 
%    (10.1250,0.4062);
%
%\end{scope}
%
%\end{tikzpicture}
%
%\caption{The dynamics of anthropomorphism. We distinguish three main phases:
%    \emph{initialization}, \emph{familiarization} and \emph{stabilization},
%    preceded by a \emph{pre-interaction} phase. In the pre-interaction phase,
%    users build an \emph{initial capital of anthropomorphism} (ICA). Once the
%    interaction starts, the level of anthropomorphism increases due to the
%    \emph{novelty effect}~\cite{kanda_interactive_2004}, and then decreases to
%    reach a \emph{stabilized level of anthropomorphism} (SLA).  During the
%    interaction, unpredicted behaviors of the robot (\emph{disruptive behaviors})
%    may lead to local increase of the level of anthropomorphism.}
%
%\label{fig:dynamics}
%\end{figure*}

@@

%\begin{figure}[htb]
%\centering
%%\resizebox{\linewidth}{!}{
%\begin{tikzpicture}
%\baselineskip=8pt
%
%\path[fill=gray!20] (0,0) rectangle (10.5,2);
%\path[fill=gray!50] (0,2) rectangle (10.5,4);
%\path[fill=gray!20] (0,4) rectangle (10.5,6);
%
%\draw (-0.3,1) node[rotate=90] {Level 1}
%      (-0.3,3) node[rotate=90] {Level 2}
%      (-0.3,5) node[rotate=90] {Level 3};
%
%\draw[->] (0,0) -- (11,0) node[anchor=north] {$t$};
%\draw[-|] (0,0) -- (0,6.5) node[anchor=east] {};
%% Us
%\draw[ultra thick, ->] (0,0) -- (1,2) -- (3,2) -- (4,4) -- (6,4) -- (7,6) --
%(9.5,6);
%\draw[ultra thick, dashed, ->] (3,2) -- (9.5,2);
%\draw[ultra thick, dashed, ->] (6,4) -- (9.5,4);
%
%\draw (11,1) node[align=left, anchor=west]{\scriptsize pre-cognitive\\\scriptsize anthropomorphism}; %label
%
%\draw (11,3) node[align=left, anchor=west] {\scriptsize{projection of existing}\\\scriptsize{mental models}\\\scriptsize{\it (familiarity)}}; %label
%
%\draw (11,5) node[align=left, anchor=west] {\scriptsize{adapted mental
%model} \\ $\to$ \scriptsize{adapted interaction}\\\scriptsize{\it (anthropomorphic or not)}}; %label
%
%
%\draw[dashed,->] (1,0.1) to[bend right] (2,1.9)  node at (4.5,1) {\tiny{\it observation (shape, motion, sound)}}; %label
%
%\draw[dashed,->] (4,2.1) to[bend right] (5,3.9)  node[align=left] at (7.5,3) {\tiny \it observation (interactive behavior) \\ \tiny \it or short interaction}; %label
%
%\draw[dashed,->] (7,4.1) to[bend right] (8,5.9)  node[align=left] at (9,5)
%{\tiny \it contextualized\\ \tiny \it interaction}; %label
%
%\end{tikzpicture}
%%}
%\caption{The three cognitive levels of anthropomorphism: Level 1 is the instinctive,
%sub-cognitive identification of living peers. {\it Empathy} is characteristic
%of this stage. After longer observation or short, non-contextualized interaction
%(typically, a lab environment), the user reaches Level 2: the user projects a
%mental model he/she is already familiar with onto the robot. After longer {\it
%contextualized} interaction (typically, at home), the user enters Level 3 of
%anthropomorphism: the user recomposes an accurate mental model of the robot,
%based on experience. This leads to adapted interaction modalities, that may
%still be anthropomorphic, or not.}
%\label{fig:cognitivemodel}
%\end{figure}

@@

\begin{itemize}
	\item \textbf{Hypothesis 2} A person's tendency to anthropomorphize a robot decreases over time and with growing experience the person has with the robot. \textit{(familiarize oneself with the robot)}
\end{itemize}

>>>>

A phenomenon that is often studied related to the human-like design of robots is
\textbf{anthropomorphism} (noted \Ant in this paper). Besides a feeling of affinity, and empathy,
anthropomorphism can be understood as being one of the resulting (and  more or
less desired) effects of the anthropomorphic design of artificial agents (up to
the first positive peak). The essence of anthropomorphism is the human user's
perception of human-likeness in the non-human agent. Logically, anthropomorphism
is said to be enhanced with increased human-like design of the agent. There are
various other reasons and explanations for why people tend to anthropomorphize
non-human agents. In general, as anthropomorphism emerges in a (real or
imagined) interaction \citep{persson_anthropomorphism_2000} between at least two
players (the human who anthropomorphizes and the non-human agent which is
anthropomorphized) there are also two main perspectives on the phenomenon: an
artifact-centered (design) and a human-centered (cognitive, psychological) one.
The Uncanny Valley hypothesis can be categorized as being part of first,
artifact-centered approach, to understand anthropomorphism.

@@

\fxnote{state here our main research hypothesis}
\fxnote{state here our main contributions}

@@

From the Roomba study, we can report on several findings related to
anthropomorphism and the anthropomorphic design of robots.
%The gathered data for these aspects include qualitative observations,
%semi-structured interviews, and also quantitative assessments of various
%aspects of human-robot interaction.
The Roomba study is one of very few long-term human-robot interaction studies in
the domestic environment.

In the following, we present findings in respect of two aspects: First, we
qualitatively describe what kinds of anthropomorphic interactions between
participants and the robot were observed and outline how these interactions
evolved over time.  Second, we present people's perception of human-likeness and
social capabilities of the robot and how this perception changed over
time.\footnote{\hl{note that these two different kinds of data
(behavior/interaction and perception) already show that we try to measure
anthropomorphism from these two angles!}}

@@

    \begin{tikzpicture}[scale=0.5, y = 2cm]
    %axis
    \draw (0,0) -- coordinate (x axis mid) (20,0);
    \draw (0,0) -- coordinate (y axis mid) (0,7);
    %ticks
    \foreach \x in {0,4,...,20}
        \draw (\x,1pt) -- (\x,-3pt);
    \foreach \y in {1,...,7} 
        \draw[black!20] (20,\y) -- (-3pt,\y);
    \foreach \y in {1,...,7} 
        \draw (-3pt, \y) node[anchor=east] {\y}; 
    %labels
    \node[below=0.8cm] at (x axis mid) {People's perception ($\sigma=15$)};
    \node at (2, -0.4) {\tiny expectations};
    \node[align=center] at (6, -0.4) {\tiny after\\ \tiny first usage};
    \node[align=center] at (10, -0.4) {\tiny after\\ \tiny 2 weeks};
    \node[align=center] at (14, -0.4) {\tiny after\\ \tiny 2 months};
    \node[align=center] at (18, -0.4) {\tiny after\\ \tiny 6 months};

    \draw[dashed, black!50] (6,0) -- (6,7) node[sloped, below, pos=0.25] {\tiny novelty effect};

    \draw[ultra thick, red!50] (2,5.6) -- (6,6.1) -- (10,6.3) -- (14,6.3) -- (18,6.1) node at (15,6.5) {\tiny \it ease of use};
    \draw[ultra thick, purple] (2,4.9) -- (6,5.2) -- (10,5.1) -- (14,4.5) -- (18,4.2) node at (3,4.7) {\tiny \it usefulness};
    \draw[ultra thick, blue!50] (2,4) -- (6,4.1) -- (10,4.6) -- (14,4.1) -- (18,4.3) node at (16,4) {\tiny \it fun};
    \draw[ultra thick, green!50] (2,3.9) -- (6,4.1) -- (10,4.2) -- (14,3.8) -- (18,3.3) node at (19,3.5) {\tiny \it intelligence};
    \draw[ultra thick, orange] (2,3.5) -- (6,4.2) -- (10,4) -- (14,3.2) -- (18,2.8) node at (14,2.7) {\tiny \it impact};

    \draw[ultra thick, dashed] (2,5.2) -- (6,5.2) -- (10,5) -- (14,4.9) -- (18,4.5) node at (14,5.3) {\tiny \it overall};

    \end{tikzpicture}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.7\columnwidth]{aibo-roomba-ipad_2.jpg}
    \caption{The Sony AIBO robotic dog (left), the iRobot Roomba vacuum-cleaning robot (middle), and the Apple Inc. iPad tablet computer (right) were compared in terms of how far users of these devices use anthropomorphic expressions in discussions about their technology / robot in online discussion forums.}
    \label{fig:aibo-roomba-ipad}
\end{figure}

@@

    	\item People engage in a more social and human-like way with a robotic pet compared to a functional robot and a tablet computer, therefore there will be a higher amount of anthropomorphic language in the AIBO and Roomba forum, compared to the iPad forum.

@@

\begin{itemize}
    \item \textit{Life-likeness}, such as being alive or having (parts of) a
        body, \eg \textit{``she can be reborn since you copied her memory
        stick''};

    \item \textit{Emotional states, empathy} or the technology having a
        \textit{feeling}, \eg \textit{``oh no, poor AIBO''};

    \item \textit{Gender, personality} or the technology having an
        \textit{intention}, \eg Roomba \textit{``seems to like to hang around
        under the sofa''};

    \item When the author gave the technology a \textit{name}, \eg
        \textit{``whenever I show Java his pink ball''};

    \item Being \textit{socially integrated}, such as being a family member, \eg
        \textit{``I'm considering adding a Roomba to the family''};

    \item \textit{Metaphorical ways}, \eg Roomba \textit{``sings its victory
        song when it finishes and docks''}.

\end{itemize}

@@

Anthropomorphism as a social phenomenon arises in an interaction \citep{persson_anthropomorphism_2000}, and thus includes at least two interaction partners (the human and the real or imagined non-human agent). Therefore, one can take two main perspectives on explaining it \citep{lee_human_2005}: a human-centered, and an artifact-centered. We briefly outline both views in the following. It has to be kept in mind that both perspectives are inseparable; they apply at the same time, and we would like to present them here just as two different viewpoints on the same kind of phenomenon.

@@

While the model primarily considers \emph{long-term interaction} -- direct
(non-mediated), repeated interaction with the same robot, over an extended
period of time (typically longer than a week) --, we also formally introduce a
so-called \emph{novelty effect}~\cite{kanda_interactive_2004} that models the
first phase of human-robot interaction, during which a specific increase of
anthropomorphic interactions is observed.

In this model, anthropomorphism is quantified by a \emph{normalized level of
anthropomorphic effects}: because anthropomorphic effects are not quantified on
an absolute scale, we present them as a normalized value, that spans from a
minimum (no anthropomorphic effects: $\ant=0$) to a maximum (noted \AntMax, with
$t_{max} = \operatorname{arg\,max}_t \, \ant[t]$). We also discuss at
section~\ref{measuring} possible methodologies for the quantitative and
qualitative assessment of anthropomorphic effects.

As pictured on Figure~\ref{fig:dynamics}, we suggest that $t_{max}$ actually
corresponds to the novelty effect peak. The actual maximum value of
anthropomorphic effects depends on each unique combination of human, robot and
several other factors we introduce below, and thus varies. The general
\emph{shape} of the model remains however the same and depicts the evolution of
anthropomorphism over time, \ie the general dynamics of anthropomorphism.

@@

\begin{figure*}[htb]
\centering

\begin{tikzpicture}[scale=1.4]

% background shading
\path[fill=blue!20] (0,0) rectangle (0.6,5.5);
\path[fill=green!20] (0.6,0) rectangle (5.2,5.5);
\path[fill=orange!20] (5.2,0) rectangle (9.8,5.5);
\draw(0,5.5) node[anchor=south west, rotate=10] {\scriptsize \sc Initialization};
\draw(2.5,5.5) node[anchor=south west, rotate=10] {\scriptsize \sc Familiarization};
\draw(6.5,5.5) node[anchor=south west, rotate=10] {\scriptsize \sc Stabilization};
% horizontal axis
\draw[->] (0,0) -- (10,0) node[anchor=north] {$t$};
\draw(5,-0.1) node[anchor=north] {\scriptsize Duration of interaction};

% vertical axis
\draw[->] (0,0) -- (0,6) node[anchor=east] {};
\draw(-0.8,3) node[rotate=90,anchor=south] {\scriptsize Normalized level of anthropomorphic effects};

\draw (-0.05, 3) -- (0.05, 3) node[anchor=east] {\ICA};
\draw (-0.05, 5) -- (0.05, 5) node[anchor=east] {\AntMax};

% vertical axis - end
\draw[->] (9.8,0) -- (9.8,2) node[anchor=east] {};
\draw (9.8, 0.8) node[anchor=west] {\SLA};

\draw[<-] (0.65,5) -- (0.8,5.2) node[anchor=east] {};
\draw (0.9,5.3) node[anchor=west] {\tiny \it novelty peak};

\draw[dotted] (0, 5) -- (6.2,5);
\draw[dotted] (0, 3) -- (6.2,3);
\draw[<->] (6.1,3) -- (6.1,5) node[anchor=east] {};
\draw (6.2,4) node[rotate=90, anchor=north, align=center] {\tiny Expectation\\\tiny mismatch};

\draw[<-] (1.7,4.4) -- (3.2,4.1) node[anchor=east] {};
\draw[<-] (2.85,2.6) -- (3.2,4.1) node[anchor=east] {};
\draw (3.2,4.1) node[anchor=west, align=center] {\tiny \it disruptive\\ \tiny
\it behaviors};
%%%%%
%% CURVES
%%%%
\begin{scope}[yscale=-1,shift={(-0.125,-0.4)}]

    \draw[ultra thick] svg[scale=1cm] "M 0.125,-2.5619582 c 0.0200733,-1.1573591
    0.33954391,-1.9982333 0.57940683,-2.0013597 0.13691605,0 0.25550329,0.052908
    0.37497897,0.1661788 0.119476,0.1130305 0.2396954,0.2786079
    0.37944,0.4790565 0.069872,0.099803 0.1021612,-0.2231749
    0.1792538,-0.2238964 0.099707,0 0.013454,0.4985362 0.3173383,0.9139831
    0.1911917,0.2612926 0.3444354,0.2578391 0.6711932,0.4894291
    0.2058265,0.1458798 0.1571532,0.9762306 0.2615031,0.9702183 0.097182,0
    0.083295,-0.3336208 0.4330446,-0.1199242 0.4306401,0.2631203
    0.216699,0.1355642 0.4296663,0.2647074 2.0858202,1.13836043
    4.34683,1.41300027 6.3741749,1.43753027";

    \draw[dashed] svg[scale=1cm] "M 0.125,-0.1952939 c 0.0553601,-3.1917862
    0.33954391,-4.3648976 0.57940683,-4.368024 0.13691605,0 0.25550329,0.052908
    0.37497897,0.1661788 m 2.6714393,2.7735737 C 4.7653984,-0.85050947
    6.5955093,0.35382293 10.125,0.4062498";

    \draw[dashed] svg[scale=1cm] "M 0.125,-3.6923825 C 0.1102888,-4.0297903
    0.46454391,-4.5601915 0.70440683,-4.5633179 M 3.7508251,-1.6235654 C
    4.9579368,-0.95548345 8.1358175,-0.82609971 10.125,-0.79459549";

\end{scope}

\end{tikzpicture}

\caption{The dynamics of anthropomorphism. We distinguish three main phases:
    \emph{initialization}, \emph{familiarization} and \emph{stabilization},
    preceded by a \emph{pre-interaction} phase. In the pre-interaction phase,
    users build an \emph{initial capital of anthropomorphism} (ICA, noted \ICA).
    Once the interaction starts, the level of anthropomorphism increases due to
    the \emph{novelty effect}, and then decreases to reach a \emph{stabilized
    level of anthropomorphism} (SLA, noted \SLA). \ICA and \SLA may vary
    depending on the user, the robot and the context of interaction.  During the
    interaction, unpredicted behaviors of the robot (\emph{disruptive
    behaviors}) may lead to local increases or decreases of the level of
    anthropomorphism.}

\label{fig:dynamics}
\end{figure*}

@@

\begin{figure}[htb]
\centering
%\resizebox{\linewidth}{!}{
\begin{tikzpicture}
\baselineskip=8pt

\path[fill=gray!20] (0,0) rectangle (10.5,2);
\path[fill=gray!50] (0,2) rectangle (10.5,4);
\path[fill=gray!20] (0,4) rectangle (10.5,6);

\draw (-0.3,1) node[rotate=90] {Level 1}
      (-0.3,3) node[rotate=90] {Level 2}
      (-0.3,5) node[rotate=90] {Level 3};

\draw[->] (0,0) -- (11,0) node[anchor=north] {$t$};
\draw[-|] (0,0) -- (0,6.5) node[anchor=east] {};
% Us
\draw[ultra thick, ->] (0,0) -- (1,2) -- (3,2) -- (4,4) -- (6,4) -- (7,6) --
(9.5,6);
\draw[ultra thick, dashed, ->] (3,2) -- (9.5,2);
\draw[ultra thick, dashed, ->] (6,4) -- (9.5,4);

\draw (11,1) node[align=left, anchor=west]{\scriptsize pre-cognitive\\\scriptsize anthropomorphism}; %label

\draw (11,3) node[align=left, anchor=west] {\scriptsize{projection of existing}\\\scriptsize{mental models}\\\scriptsize{\it (familiarity)}}; %label

\draw (11,5) node[align=left, anchor=west] {\scriptsize{adapted mental
model} \\ $\to$ \scriptsize{adapted interaction}\\\scriptsize{\it (anthropomorphic or not)}}; %label

\draw[dashed,->] (1,0.1) to[bend right] (2,1.9)  node at (4.5,1) {\tiny{\it observation (shape, motion, sound)}}; %label

\draw[dashed,->] (4,2.1) to[bend right] (5,3.9)  node[align=left] at (7.5,3) {\tiny \it observation (interactive behavior) \\ \tiny \it or short interaction}; %label

\draw[dashed,->] (7,4.1) to[bend right] (8,5.9)  node[align=left] at (9,5)
{\tiny \it contextualized\\ \tiny \it interaction}; %label

\end{tikzpicture}
%}
\caption{The three cognitive levels of anthropomorphism: Level 1 is the instinctive,
sub-cognitive identification of living peers. {\it Empathy} is characteristic
of this stage. After longer observation or short, non-contextualized interaction
(typically, a lab environment), the user reaches Level 2: the user projects a
mental model he/she is already familiar with onto the robot. After longer {\it
contextualized} interaction (typically, at home), the user enters Level 3 of
anthropomorphism: the user recomposes an accurate mental model of the robot,
based on experience. This leads to adapted interaction modalities, that may
still be anthropomorphic, or not.}
\label{fig:cognitivemodel}
\end{figure}

@@

\begin{itemize}
    \item \textbf{Hypothesis 1} A person's tendency to anthropomorphize a robot
        is impacted by the context of use and purpose of the robot. A social
        context and purpose of the robot increases anthropomorphism.
        \textit{(context and purpose of the robot)}
	\item \textbf{Hypothesis 2} A person's tendency to anthropomorphize a robot decreases over time and with growing experience the person has with the robot. \textit{(familiarize oneself with the robot)}
\end{itemize}
